Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-06-25 paper/paper.tex
A few small changes

Our model consists of agents, representing axonal growth cones, originating
from a square retina and moving upon a square tectum. Each agent carries a set
of 4 receptors and 4 ligands which are expressed at differing levels depending
upon the soma's location on the retina. The expression levels of the receptors
and ligands form gradients across the retinal surface. Receptors are arranged
in orthogonal pairs with $r_0$ being orthogonal to $r_1$ and $r_2$, whose
gradient is opposite to $r_0$ is orthogonal to $r_3$. Ligands are also
arranged in orthogonal pairs, with...
%
Similarly, the tectum expresses the same sets of
receptors and ligands, also in orthogonal pairs of gadients, though not
necessarily with the same expression function.

>>>>

Our model consists of agents, representing axonal growth cones, originating
from a square retina and moving upon a square tectum. Each agent carries a set
of 4 receptors and 4 ligands which it expresses at differing levels depending
upon the soma's origin on the retina. The expression levels of
the receptors and ligands form gradients across the retinal surface. Receptors
are arranged in orthogonal pairs with $r_0$ being orthogonal to $r_1$ and
$r_2$, whose gradient is opposite to $r_0$ is orthogonal to $r_3$. Ligands are
also arranged in orthogonal pairs, with...
%
The tectum expresses the same sets of receptors and ligands, also in
orthogonal pairs of gradients, though not necessarily with the same expression
function.
